Ingredients

\begin{itemize}
	\item 8 ounces elbow macaroni
	\item 1 tablespoon plus $\nicefrac{1}{2}$ teaspoon kosher salt, divided
	\item 3 tablespoons unsalted butter
	\item 3 tablespoons all-purpose flour
	\item 1 tablespoon ground mustard
	\item 1 teaspoon smoked or regular paprika
	\item 3 cups half and half
	\item 4 ounces sharp cheddar cheese, grated
	\item 5 ounces Monterey jack cheese, grated
	\item $\nicefrac{1}{2}$ teaspoon freshly ground black pepper
\end{itemize}

\noindent
Topping

\begin{itemize}
	\item 3 ounces Monterey jack cheese, grated
	\item 3 tablespoons unsalted butter, melted
	\item 1 cup panko breadcrumbs
\end{itemize}

\noindent
Directions
\newline

Heat oven to $350^\circ$F. Grease 4-quart casserole or souffl\'{e} dish and set aside.

Place dry pasta + 1 tablespoon of salt in 4-quart pot and barely cover with cold water. Bring to a boil over high heat, stirring occasionally. Test for al dente, 9 to 10 minutes. Drain pasta in a colander but do not rinse.

Melt butter in 3-quart saucepan over medium heat. Whisk in the flour and cook, stirring occasionally, until mixture is pale blond, ~3 minutes. Whisk in mustard + paprika, and cook until aromatic, ~1 minute. Whisk in milk, increase the heat to medium-high, whisking often, until mixture is slightly thickened, 7 to 8 minutes. Remove from heat. Stir in cheese, remaining salt, and pepper. Fold in macaroni and move to the prepared dish.

Sprinkle with remaining cheese. Toss breadcrumbs with melted butter and distribute evenly over the top. Bake until golden on top, but not dried out, 15 to 20 minutes. Cool for 5 minutes, then serve to a grateful world.

Yields 6 servings.