Ingredients

\begin{itemize}
	\item 1 lb Chicken Breast
	\item 16 oz Heavy Cream
	\item 3/4 Cup Parmesan Cheese (Shredded)
	\item 1 Can Italian Style Stewed Tomatoes
	\item 4 Scallions
	\item 3-4 cloves Garlic
	\item 8 oz Fettuccine Pasta
	\item Oregano or Basil
\end{itemize}

\noindent
Directions
\newline

Begin by heating a frying pan to medium heat, and apply just enough oil to cover the entire pan. Butterfly the chicken breasts to increase surface area, and cook in frying pan just to get a slight browning of the chicken, approximately 3 to 5 minutes or so on each side. Once finished, place the chicken breasts into a Crockpot, and evenly distribute them.

Cut the stems off of the scallions, dice them, and sprinkle them on top of the chicken. Dice and add the garlic cloves to the Crockpot as well. Strain the tomatoes in a colander, dice them, and add them to the Crockpot. Add a few dashes of oregano or basil, as well as salt, pepper, and any other spices you wish. Turn Crockpot on to its \textit{low} setting, and let sit for 6-7 hours, stirring every few hours or so. When the chicken is tender and falling apart, it's done.

Once the chicken is cooked, take it out and dice it into small bite-size pieces, and place back into the colander. Add the heavy cream and Parmesan cheese to the Crockpot, stir, and set heat to its \textit{high} setting. Cook the fettuccine pasta to \textit{Al Dente}, strain, and add the noodles to the Crockpot. Mix, and let cook for an additional 30 minutes. Serve and enjoy!